---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# curatoR

<!-- badges: start -->
<!-- badges: end -->

The goal of curatoR is to provide an accessible way for biologists to curate biological datasets.
Specifically, the package provides functions to flag suspicious observations based on location,
name, and species. It also provides an easy way to map observations.

## Installation

You can install the development version of curator from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("matthewbradley22/curator")
```


## Documentation:

For an in depth example of the curatoR package, visit https://matthewbradley22.github.io/curator/articles/curator.html

## Example

This is a basic example of retriving data from gbif, flagging it with CoordinateCleaner (flag_data), and flagging any species names in the data that do not occur in the example ECD provided in the package (flag_names).

```{r example, message=FALSE, warning=FALSE, results = FALSE}
library(curator)

#Retrieve data with rgbig::occ_search and pass to CoordinateCleaner::clean_coordinates
data = occ_since(numObs = 500)
flags = flag_data(data)
```

The column names that begin with a period (seen after summary(flags) below) each indicate the number of observations that have a certain flag.
```{r}
#Flag names that do not occur in ECD
flags = flag_names(flags, curator::ECD)
summary(flags)
```

Once flagged we can map this data and color it by presence and type of flags, as seen below.

## Example dynamic map:

[Dynamic map example](https://matthewbradley22.github.io/curator/curatorExample.html)

