---
title: "Introduction to curatoR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to curatoR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(curator)
```

## Overview:

curatoR was designed to help biologists pull data from GBIF and curate it quickly. GBIF data is messy, and manually curating it is time consuming. curatoR allows biologists to use an existing Expert Curated Dataset (ECD) to filter GBIF data and easily update the ECD.

## Workflow
### Retrieving data:

The first step of the workflow is done using the "occ_since" function which allows a user to pull GBIF data of a certain taxon since a certain date. This function defaults to pulling all Carex data since June 2021. Note that the function defaults to pulling all data (up to 1,000,000 occurrences) since the date, and this step can be quite slow. 

```{r}
dat = occ_since(numObs = 1000)
head(dat)
```

### Load ECD:

The user should load an ECD dataset into R. For this example I will use an example ECD that comes with curatoR and contains 50,000 Carex observations
```{r}
data(ECD)
head(ECD)
```

### Initial Flags:
The first step of cleaning data uses a function that wraps the CoordinateCleaner:clean_coordinates function and creates an object with the original dataframe, as well as new columns that indicate flags. This object will be used for the rest of the workflow.

```{r message=FALSE, warning=FALSE}

flagged <- flag_data(dat)
summary(flagged)

```

### Label continents:

In the coming flagging functions, it will be necessary to have the continents labeled for each occurrence. Our ECD has a country code column that is named differently than the default, so I specify the name of the column.

```{r}
flagged$continent <- get_continents(flagged)
ECD$continent <- get_continents(ECD, country = "CountryCode")

head(flagged$continent)
```

### Flagging Countries:

The next step is to flag any occurrences in which the species is in a country in which it does not occur in the ECD. For each of these new flagging steps the user can pass the whole "Flagged" object from above, and can indicate any column names if they differ from the expected names.

```{r}
#Can see new .country column in the summary of flagged.
flagged <- flag_countries(flagged, ECD, ECDcountry = "CountryCode")
summary(flagged)

#We can see which species-nations combiantions are causing these flags
unique(flagged[flagged$.country == F,][c("species", "countryCode")])
```

### Flagging Convex Hulls:

Next, for each species-continent combination, we can build a convex hull (a species on 3 different continents will have 3 separate convex hulls) and flag species that occur outside of these convex hulls.

```{r}

flagged <- flag_convex_hull(flagged, ECD)
summary(flagged)

```

### Flagging based on distance

Next, for each species-continent combination, we flag occurrences of any species that are over 2 standard deviations from the center of the distribution.
```{r}

flagged <- flag_distance(flagged, ECD)
summary(flagged)

```

### Flagging Names

The last flag added is for any species names that do not occur in the ECD. These names can then be matched up to an online database in an effort to fix them.

```{r}



```
